An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-05 jmiv.tex
Fix image in figure 11
int(C2) included in int(C1)

\begin{definition}[Glued Curve]
Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_1) \subset int(C_2)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$. The linels $\ell_1,\ell_2$ are called junction linels.
\end{definition}

@@

 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/lg0_sq0_dt1_it20.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg1_sq0_dt1_it50.png} &
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg2_sq0_dt1_it50.png} \\

>>>>

\begin{definition}[Glued Curve]
Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_2) \subset int(C_1)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$. The linels $\ell_1,\ell_2$ are called junction linels.
\end{definition}

@@

 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/grabcut-seg.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg1_sq0_dt1_it50.png} &
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg2_sq0_dt1_it50.png} \\
